Effects of epidemiological structure on the transient evolution of HIV virulence

### 2017-02-01 ms/cover_letter/plosHIVcover_resubm2.tex
working on cover letter

\todo{ADD GENERAL POINTS HERE}

@@

\textbf{Editor}

\revcomment{
In particular, we would encourage you to take into consideration the remarks of reviewer 1 on the presentation of your work. Furthermore, reviewer 3 raises important points regarding the limitation of the ODE equation approach. While you already discuss some of these points, it would be great if you put your study into the context of more realistic modeling approaches of HIV and other sexually transmitted diseases. It would also be insightful if you discussed to what extent your "heterogeneous" model covers age and sex structure.
}

@@

\revcomment{
The outstanding issue is that the paper remains quite challenging to
read. It is just not written as clearly as it could be. In many
paragraphs, the authors launch into discussion of complex points with
long, multi-clause sentences, instead of explaining their motivation
and results in simple, concise phrases. Too often the authors do not
make it clear WHY they did something. Reading the original papers by
Fraser’s group on this topic (PNAS 2007 and PLoS Comp Biol 2011)
provide good examples of clear writing.
}
%\response{}

@@

\response{
We agree with the reviewers that this is a ``rather theoretical'' finding,
but we think it is important and useful nonetheless.  As we mention
in the discussion, the decision to examine the effects of contact
structure does not mean we can feel free to ignore all other aspects
of epidemiological realism; on the other hand, data for
parameterization and time for building and checking models is
limited, so we have to prioritize in some way. We would argue that
both quantifying the effects of contact structure and understanding
how they work is a useful, albeit incremental, step toward reliable
models of HIV eco-evolutionary dynamics.
}

>>>>

We are happy to have the chance to revise our manuscript
(and thank you for your patience while we've taken a little
longer than average to do so). Besides general clarification,
some of the main changes are that we
\begin{itemize}
  \item added a figure illustrating the main model structures we use
  \item switched our primary descriptor of viral evolution back to SPVL, as recommended by reviewer \#1
  \item implemented vital dynamics and heterogeneity in conjunction
with each of our four 'base' models (i.e., models with and 
without instantaenous switching, with and without extra-pair contact); 
the detailed results for these models are given in the supplementary materials, but
we do comment on the results in the main text.
\end{itemize}

We look forward to your decision on the revised version.

@@

@@

\revcomment{
The outstanding issue is that the paper remains quite challenging to
read. It is just not written as clearly as it could be. In many
paragraphs, the authors launch into discussion of complex points with
long, multi-clause sentences, instead of explaining their motivation
and results in simple, concise phrases. Too often the authors do not
make it clear WHY they did something. Reading the original papers by
Fraser’s group on this topic (PNAS 2007 and PLoS Comp Biol 2011)
provide good examples of clear writing.
}
\response{This is a very general comment, but we have gone
through the entire manuscript and tried to clarify it.}

@@

\response{
We agree with the reviewers that this is a ``rather theoretical'' finding,
but we think it is important and useful nonetheless.  As we mention
in the discussion, the decision to examine the effects of contact
structure does not mean we can feel free to ignore all other aspects
of epidemiological realism; on the other hand, data for
parameterization and time for building and checking models is
limited, so we have to prioritize in some way. We would argue that
both quantifying the effects of contact structure and understanding
how they work is a useful, albeit incremental, step toward reliable
models of HIV eco-evolutionary dynamic.
}
